\documentclass[11pt,a4paper,twoside]{article}
\usepackage{theme/lmuthesis}

\usepackage{listings}
\usepackage{xcolor}

%New colors defined below
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% this for draft water mark
\input{condition}
\ifthenelse{\boolean{release}}{
}{
    \usepackage{draftwatermark}
    \SetWatermarkText{DRAFT}
    \SetWatermarkScale{1}
}

% meta informations
\department{Institut f\"ur Informatik}
\lfe{Lehr- und Forschungseinheit Medieninformatik}
\professor{Prof.\ Dr.\ Heinrich Hussmann}
\type{Master's Thesis}
\title{Explanation Adaptation for Hybrid Multimedia Recommendation System}
\author{Zhe Li}
\email{Li.Zhe@campus.lmu.de}
\bearbeitungszeitraum{02.08.2019 to 02.03.2020} 
\supervisor{Zhiwei Han and Yuanting Liu}
\taskdescription{
    \begin{description}
        \item[THESIS TITLE] Explanation Adaptation for Hybrid Multimedia Recommendation System
        \item[Problem Statement] How to make the explainable recommendation system interact with the user in a transparent and efficient way
        \item[Tasks] Build a hybrid movie recommendation system to compare some different ways of recommendation styles and design an adaptation style for the recommendation by using an explanation template.
        \item[Keywords] Recommendation System, Explainable Recommendation, Explanation Adaptation, Graph Neural Network, UMNN
    \end{description}
}
\acknoledgement{
\par First of all, I would like to appreciate my supervisor Zhiwei Han and Yuanting Liu for their valuable advice on my thesis. They gave me goals and directions for finishing my thesis.
\par And I would like to appreciate Prof.Andreas Butz and Prof.Heinrich Hussmann, their rigorous academic attitude and profound knowledge, the unpretentious and approachable personality charm have a profound influence on me, and it is my role model to learn.
\par And I would like to appreciate my parents for help during my studies, with funding and love. Finally, I would like to say thanks to all my friends who accompanied me during my master studies and thank them for all the helpful suggestions and opinions they provided for me.
}
\abstract{
    With the development of communication technology and data science, the relationship between people and information has evolved from one-way, people looking for information, to the current two-way relationship. The recommendation system plays a more important role in it. An explainable recommendation system can interact with users in a transparent and efficient way. We build a hybrid movie recommendation system to compare some different ways of recommendation styles and design an adaptation style for the recommendation by using an explanation template. And we propose a new methodology for the "adaptation rule" of recommendation explanation. A new bipartite graph-based algorithm is designed to represent our user-movie network.
}

\begin{document}

\makecover
\maketaskdescription
\makededication
\makeabstract
\maketoc
% optional:
\listoffigures
\listoftables
\listofalgorithms
\lstlistoflistings

\cleardoublepage

\input{src/ch01-intro}
\input{src/ch02-related-work}
\input{src/ch03-system-design}
\input{src/ch04-experiment}
\input{src/ch05-evaluation}
\input{src/ch06-discussion}
\input{src/ch07-conclusion}

\input{src/ch08-appendix}
\input{literatures/bib.tex}

\end{document}